\huge Tor's Usability for Censorship Circumvention

### 2016-05-10 pets2017-paper/pets2017-paper.tex
fix numbers from deleting P57 and reword accordingly. Added median active times to table 2.

\subsection{Results} 
Out of our 124 recruited participants, 115 provided valid data. We have 58 participants who tested the new interface, and 58 who tested the old interface. 38 participants were in E1, 37 participants were in E2, and 40 participants were in E3.
Table~\ref{table:participant-summary} summarizes the rate of success and time to success for our participants' based on their interface version and environment combination.

\begin{table}
\centering
	% Generated by info.R.
	\begin{tabular}{l r r r r}
	& \multicolumn{2}{c}{success rate} & \multicolumn{1}{c}{median time} \\
	& \multicolumn{2}{c}{after 40 minutes} & \multicolumn{1}{c}{to success} \\
	\noalign{\hrule}
	E1-NEW & 19/19 & 100\% & 0:20 \\
	E1-OLD & 19/19 & 100\% & 1:01 \\
	E2-NEW & 18/18 & 100\% & 3:22 \\
	E2-OLD & 16/19 & 84\% & 5:00 \\
	E3-NEW & 13/20 & 65\% & 20:56 \\
	E3-OLD & 10/20 & 50\% & 40:08 \\
	\end{tabular}
\caption{
A summary of participants' success in circumventing censorship
given their simulated censorship environment and version of Tor. Those who
failed to connect successfully were assigned the maximum time of 40:08.
}
\label{table:participant-summary}
\end{table}

@@

\subsubsection{Time to Success} 
The median times to completion for participants of the new interface are less than those with the old interface (Table~\ref{table:participant-summary}). Non-finishing participants are assigned the maximum time of 40:08
for the purpose of computing the median. However, the difference between the medians times to success between new versus old interfaces, in aggregate and in censorship environment, are not statistically significant. The level of censorship, rather than the interface, had a significant impact on the time to success. 
%The more difficult the censorship environment, the longer participants took to configure their connection (Kruskal--Wallis $\chi^2 = 80.926$, $\mbox{df} = 2$, $p < 10^{-15}$). 
The distribution of participants' time to success can be seen in Fig.~\ref{fig:time_to_success_clamped}.
%impact of version on time to success: not significant ($W = 1569$, $p = 0.07796$)
%impact of env on time to success : significant (Kruskal--Wallis $\chi^2 = 80.926$, $\mbox{df} = 2$, $p < 10^{-15})

\begin{figure}[t]
\centering
\includegraphics{time_to_success_clamped}
\caption{
Time to first success, by censorship environment and interface.
The dots show the raw completion times,
while the boxplots show the medians and interquartile ranges.
The ``DNF'' figures at the right show the number of participants 
who did not finish in the time allotted.
Here, non-finishing participants are assigned the maximum time of 40:08
for the purpose of computing the median.
}
\label{fig:time_to_success_clamped}
\end{figure}

@@

\subsubsection{Active Configuration Time} 
We summarize each participant's actions throughout the experiment in Fig.~\ref{fig:all-participant-edges}. Each row in Fig.~\ref{fig:all-participant-edges} corresponds to a participant. The bar represents a path through the interface, illustrating time spent on each screen, transitions between screens, how many attempts were made, and if they were eventually successful.

@@

\begin{figure}[t]
\centering
\includegraphics{time_to_success_active_clamped}
\caption{
Active configuration time, by censorship environment and interface.
The dots show the raw active configuration times,
while the boxplots show the medians and interquartile ranges.
Here, non-finishing participants' active time was computed by
subtracting the amount of time spent on the progress screen from the 
the maximum time of 40:08.
}
\label{fig:time_to_success_active_clamped}
\end{figure}

@@

Perhaps a more meaningful measurement of time is the amount of time participants actively configured their connection (Figure~\ref{fig:time_to_success_active_clamped}). We define this as the time that participants spent interacting with the interface, excluding the time waiting for the connection to bootstrap. Active configuration time for unsuccessful participants were calculated by subtracting the amount of time spent on the progress screen from the maximum experiment time, 40 minutes. This is an approximation, since some participants searched for help on the web after exiting the interface or on the progress screen.

We performed a one-tailed Mann--Whitney test to compare the amount of active configuration time between participants who used the new interface and the participants who used the old interface. The new interface results a statistically significant reduction in active configuration time. (Mann--Whitney $Z = -2.7$, $p = 0.0032$, $r= 0.25$). The small effect size may be due to the fact that the reduction in time mostly applied to participants in E3.

@@

\begin{description}
%connect vs configure
\item {\bfseries Users try the easy path first.} Users try the easy option of connecting directly to the Tor network first. This leaks to network eavesdroppers leaking that they are connecting to Tor.  81\% (93 of 115) of first attempts were to connect directly, 53\% (49 of 115) from the new interface and 47\% (44 of 115) from the old interface.

@@

\begin{description}
\item {\bfseries Automate configuration after failure.} After one unsuccessful attempt, a user has already leaked to network eavesdroppers leaking that they are connecting to Tor. Automating the configuration process thereafter will have no increase in risk. This will specifically help users that will never try to configure their connection (the most common failure case) to succeed and drastically reduce the time spent for the {\color {red} 64\%} of participants who failed their first attempt. Users in more comprehensive censorship environments are more likely to benefit from this, as 5\% of participants in the mild censorship environment, {\color {red} 84\%} participants in intermediate censorship environment, and 100\% of participants in the heavy censorship environment failed the first time.
\item{\bfseries Hide infrequently used options.} Telling users they did not need a proxy was not enough to deter users from configuring a proxy. Only a small fraction of the Internet population requires a proxy to connect to the Internet. Hiding the proxy screen by default and only showing it after it has been detected as necessary might improve the user experience focusing user effort on configuring bridges.
\item {\bfseries Be explicit about recommendations.} Many do not know what to do after the recommended bridge failed. The interface should mark which bridges have been tired before and recommend the user to try another bridge. (i.e. After a user tried an obfs3 bridge, the interface updates its recommendation to a meek bridge and mark the obfs3 bridge with an ``X''.)
\item{\bfseries Set a timeout on the progress bar.} Informing users that they have failed earlier will decrease the overall time to success, create an opportunity to give suggestions, and reduce user frustration. 
\item{\bfseries Have a user-tolerant bridge auto-responder.} The bridge auto-responder responds to user requests for custom bridges. Users can make this request by emailing bridges@torproject.org with a non-empty title and ``get bridges'' in the body. Both of our users who tried to get custom bridges this way failed to format their request correctly. Having the auto-responder respond with bridges as a default or recovering from common errors (such as typing ``get bridges'' in the subject line) may help users succeed. 
\end{description}

@@

%success rate and version
Each participant had a boolean variable indicating a successful connection to Tor. Rates of success were calculated by dividing the number of participants who succeeded the condition over the total number of participants in the condition. This gave us six rates of success. E1-NEW, E2-NEW, and E3-NEW rates of success were compared against E1-OLD, E2-OLD, and E3-OLD.  We used a Pearson's Chi-squared test to test the significance of success rates. The difference between success rates of participants with the new interface and participants with the old interface was not significant (X-squared = 0.012599, df = 2, p-value = 0.9937).

%time to success and version
Time to success was measured as the time from the participants started the Tor launcher interface to the first successful bootstrap to the Tor network. This measurement was 1) non-normal and heavily right-tailed since participants were less and less likely to succeed as time went on and 2) right-censored at 40 minutes, the maximum time of the experiment. Because of the right-tailed nature of the data, we used a one-tailed Mann--Whitney test. Because the Mann--Whitney test does not account for right-censored data, we assigned the participants who did not succeed the maximum time of 40 minutes for the purpose of this test. We do not find the difference of times to success between participants with the new interface and participants with the old interface to be significant (Z = -1.5451, p-value = 0.06116).

%active time and version
Active configuration time was measured as the time the participants spent in the Tor launcher interface, except for the time spent the progress screen. For our participants who did not succeed to connect to Tor, subtracted the time spent on the progress screen from the maximum experiment time of 40 minutes. This measurement was also 1) non-normal and heavily right tailed and 2) impacted by right-censored measurement of time to success. Because of the right-tailed nature of the data, we used a one-tailed Mann--Whitney test. We do find the difference of active configuration times between participants with the new interface and participants with the old interface to be significant (Z = -3.4069, p-value = 0.0003286).

>>>>

\subsection{Results} 
The possible interface version and environment combinations resulted in 6 experimental conditions. We recruited 124 participants to aim for about 20 participants per condition. We filtered participants who downloaded their own version of Tor Browser or did not sign the consent form, resulting in 115 participants. Table~\ref{table:participant-summary} summarizes the rate of success, time to success, and active time for our participants' by condition.

\begin{table}
\centering
	% Generated by info.R.
	\begin{tabular}{l r r r r r}
	& \multicolumn{2}{r}{success rate} & \multicolumn{1}{r}{median time} &\multicolumn{1}{r}{median}\\
	& \multicolumn{2}{r}{after 40 minutes} & \multicolumn{1}{r}{to success} & \multicolumn{1}{r} {active time} \\
	\noalign{\hrule}
	E1-NEW & 19/19 & 100\% & 0:20 & 0:06 \\
	E1-OLD & 19/19 & 100\% & 1:01 & 0:24 \\
	E2-NEW & 18/18 & 100\% & 3:22 & 0:40 \\
	E2-OLD & 16/19 & 84\% & 5:00 & 2:04 \\
	E3-NEW & 13/20 & 65\% & 20:56 & 1:53 \\
	E3-OLD & 10/20 & 50\% & 40:08 & 9:06 \\
	\end{tabular}
\caption{
A summary of participants' success in circumventing censorship
given their simulated censorship environment and version of Tor. Those who
failed to connect successfully were assigned the maximum time of 40:08.
}
\label{table:participant-summary}
\end{table}

@@

\subsubsection{Time to Success} 
Time to success is defined as the time until the first successful connection to Tor. Non-finishing participants are assigned the maximum experiment time of 40:08.  Our changes to the interface had a significant impact in reducing the time participants took to successfully connect to Tor (Mann--Whitney $ Z = -1.69$, $p < 0.05$, $r= 0.158$). The simulated censorship environment also had an impact; the more difficult the censorship environment, the longer participants took to configure their connection (Kruskal--Wallis $\chi^2 = 80.926$, $\mbox{df} = 2$, $p < 10^{-15}$). 
Table~\ref{table:participant-summary} shows the median active times and Figure~\ref{fig:time_to_success_clamped} shows their distribution.

\begin{figure}[t]
\centering
\includegraphics{time_to_success_clamped}
\caption{
Time to first success, by censorship environment and interface.
The dots show the raw completion times,
while the boxplots show the medians and interquartile ranges.
The ``DNF'' figures at the right show the number of participants 
who did not finish in the time allotted.
Here, non-finishing participants are assigned the maximum time of 40:08.
}
\label{fig:time_to_success_clamped}
\end{figure}

@@

\subsubsection{Active Time} 
We summarize each participant's actions throughout the experiment in Fig.~\ref{fig:all-participant-edges}. Each row in Fig.~\ref{fig:all-participant-edges} corresponds to a participant. The bar represents a path through the interface, illustrating time spent on each screen, transitions between screens, how many attempts were made, and if they were eventually successful.

@@

\begin{figure}[t]
\centering
\includegraphics{time_to_success_active_clamped}
\caption{
Active time, by censorship environment and interface.
The dots show the raw active configuration times,
while the boxplots show the medians and interquartile ranges.
Here, non-finishing participants' active time was computed by
subtracting the amount of time spent on the progress screen from the 
the maximum time of 40:08.
}
\label{fig:time_to_success_active_clamped}
\end{figure}

@@

Perhaps a more meaningful measurement is the amount of time participants actively configured their connection (Figure~\ref{fig:time_to_success_active_clamped}). We define active time as the time that participants spent interacting with the interface, excluding the time waiting for the connection to bootstrap. Active time for unsuccessful participants were calculated by subtracting the amount of time spent on the progress screen from the maximum experiment time, 40 minutes. This is an approximation, since some participants searched for help on the web after exiting the interface or on the progress screen.

We performed a one-tailed Mann--Whitney test to compare the amount of active configuration time between participants who used the new interface and the participants who used the old interface. Our changes to the interface reduced the time participants spent configuring the interface (Mann--Whitney $Z = -3.29$, $p < 0.0005$, $r = 0.307$). Table Table~\ref{table:participant-summary} shows the median active times and Figure~\ref{fig:time_to_success_active_clamped} shows their distribution.

@@

\begin{description}
%connect vs configure
\item {\bfseries Users try the easy path first.} Users generally try connecting directly to the Tor network first. 81\% (93 of 115) of first attempts were to connect directly, with 53\% (49 of 93) direct first attempts from the new interface and 47\% (44 of 93) direct first attempts from the old interface. This leaks to network eavesdroppers that they are connecting to Tor.

@@

\begin{description}
\item {\bfseries Automate configuration after failure.} After one unsuccessful attempt, a user has already leaked to network eavesdroppers leaking that they are connecting to Tor. Automating the configuration process thereafter will have no increase in risk. This will specifically help users that will never try to configure their connection (the most common failure case) to succeed and drastically reduce the time spent for the 63\% of participants who failed their first attempt. Users in more comprehensive censorship environments are more likely to benefit from this, as 5\% of participants in the mild censorship environment, 84\% participants in intermediate censorship environment, and 100\% of participants in the heavy censorship environment failed the first time.
\item{\bfseries Hide infrequently used options.} Telling users they did not need a proxy was not enough to deter users from configuring a proxy. Only a small fraction of the Internet population requires a proxy to connect to the Internet. Hiding the proxy screen by default and only showing it after it has been detected as necessary might improve the user experience focusing user effort on configuring bridges.
\item {\bfseries Be explicit about recommendations.} Many do not know what to do after the recommended bridge failed. The interface should mark which bridges have been tired before and recommend the user to try another bridge. (i.e. After a user tried an obfs3 bridge, the interface updates its recommendation to a meek bridge and mark the obfs3 bridge with an ``X''.)
\item{\bfseries Set a timeout on the progress bar.} Informing users that they have failed earlier will decrease the overall time to success, create an opportunity to give suggestions, and reduce user frustration. 
\item{\bfseries Have a user-tolerant bridge auto-responder.} The bridge auto-responder responds to user requests for custom bridges. Users can make this request by emailing bridges@torproject.org with a non-empty title and ``get bridges'' in the body. Both of our users who tried to get custom bridges this way failed to format their request correctly. Having the auto-responder respond with bridges as a default or recovering from common errors (such as typing ``get bridges'' in the subject line) may help users succeed. 
\end{description}

@@

%success rate and version
Each participant had a boolean variable indicating a successful connection to Tor. Rates of success were calculated by dividing the number of participants who succeeded the condition over the total number of participants in the condition. This gave us six rates of success. E1-NEW, E2-NEW, and E3-NEW rates of success were compared against E1-OLD, E2-OLD, and E3-OLD.  We used a Pearson's Chi-squared test to test the significance of success rates. The difference between success rates of participants with the new interface and participants with the old interface was not significant ($X^2 = 0.0126$, $df = 2$, $p = 0.994$).

%time to success and version
Time to success was measured as the time from the participants started the Tor launcher interface to the first successful bootstrap to the Tor network. This measurement was 1) non-normal and heavily right-tailed since participants were less and less likely to succeed as time went on and 2) right-censored at 40 minutes, the maximum time of the experiment. Because of the right-tailed nature of the data, we used a one-tailed Mann--Whitney test. Because the Mann--Whitney test does not account for right-censored data, we assigned the participants who did not succeed the maximum time of 40 minutes for the purpose of this test. We do not find the difference of times to success between participants with the new interface and participants with the old interface to be significant ($ Z = -1.69$, $p = 0.0454$, $r= 0.158$).

%active time and version
Active configuration time was measured as the time the participants spent in the Tor launcher interface, except for the time spent the progress screen. For our participants who did not succeed to connect to Tor, subtracted the time spent on the progress screen from the maximum experiment time of 40 minutes. This measurement was also 1) non-normal and heavily right tailed and 2) impacted by right-censored measurement of time to success. Because of the right-tailed nature of the data, we used a one-tailed Mann--Whitney test. We do find the difference of active configuration times between participants with the new interface and participants with the old interface to be significant ($Z = -3.29$, $p = 0.000493$, $r = 0.307$).
